Reading Notes

### 2020-02-12 paper.tex
trying to form a habit. mornings are hard
habit :) tomorrow reskim existing paper

>>>>

got busy with fancy-ing up the GIXStapose repo, helping rachel, office hours, and atom-typing with gaff-foyer with ryan and chris. Briefly skimmed the chakraborty paper-- they consider all possible mappings that a cg compound can have in order to systematically pick a cging scheme.
OK Chakraborty notes:
-exclude cg mapping schemes to those that maintain symmetry
-Zhang and Voth designed CG mapping operators by preserving "essential dynamics"
-Cao and Voth worked on centering functions COM vs center of charge. They found center of change was better for preserving intermolecular structure.
-Wagner generalize centering functions to arbitrary thermodynamic quantities
-Marrink grouped four heavy atoms and showed that this simple consistent scheme works.
CG models are validated by preservation of rdfs and velocity autocorrelation functions (vacfs)
mapping operator tree
